---
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
output:
  word_document:
    reference_docx: word_format.docx
---

```{r setup, include = F, warning = F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

# Supporting Information for: Non-random dispersal in sympatric stream fishes: influences of natural disturbance and body size

**Author**: Akira Terui^1^, Seoghyun Kim^1,2,3^, Kasey Pregler^2,3^, Yoichiro Kanno^2,3,4\*^

**Journal:** Freshwater Biology

**This file includes:**

-   Tables S1 - S4

-   Figures S1 - S6

^1^ 321 McIver Street, Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27402-6170, USA

^2^ 1474 Campus Delivery, Department of Fish, Wildlife, and Conservation Biology, Colorado State University, Fort Collins, CO, 80523-1474, USA

^3^ 261 Lehotsky Hall, Department of Forestry and Environmental Conservation, Clemson University, Clemson, SC, 29634, USA

^4^ 1474 Campus Delivery, Graduate Degree Program in Ecology, Colorado State University, Fort Collins, CO, 80523-1474, USA

\*Corresponding author: Yoichiro Kanno

email: [Yoichiro.Kanno\@colostate.edu](mailto:Yoichiro.Kanno@colostate.edu){.email}

\pagebreak

**Table S1** Descriptive statistics for the mark-recapture data of bluehead chub, creek chub, and striped jumprock. *Unique* individuals captured or recaptured are the number of individuals excluding repeated counts of the same individuals. *Total replicate* is the total number of individuals captured or recaptured, including repeated counts of the same individuals.

```{r table_1, results='asis'}
source("si_table_mr_summary.R")
```

\pagebreak

**Table S2** Comparison of Widely Applicable Information Criterion (WAIC) between models that use the high flow (the occurrence of flow events exceeding the 99th percentile of daily water levels) and the median water level as a metric of streamflow conditions.

```{r, results='asis'}
source("si_table_waic.R")
```

\pagebreak

**Table S3** Parameter estimates of the Bayesian dispersal model that uses "high flow" as a measure of stream flows (the occurrence of flow events exceeding the 99th percentile of daily water levels). Median estimates and the associated 95% credible intervals (95% CI) were reported.

```{r, results='asis'}
source("si_table_est_q99.R")
```

**Table S4** Parameter estimates of the Bayesian dispersal model that uses median water level as a measure of stream flows (instead of the occurrence of flow events that exceeded the 99th percentile of daily water levels during the whole study period). Median estimates and the associated 95% credible intervals (95% CI) were reported.

```{r, results='asis'}
source("si_table_est_q50.R")
```
