---
title: "Supporting Information"
author: Akira Terui, Seoghyun Kim, Kasey C. Pregler, Yoichiro Kanno
output:
  pdf_document:
    toc: true
    toc_depth: 3
    template: default
---
### Overview
This PDF file is supporting information for "Non-random dispersal in sympatric stream fishes: influences of natural disturbance and body size". This includes:

* Tables S1 - Descriptive statistics for the mark-recapture data in Indian Creek
* Tables S2 - Descriptive statistics for the mark-recapture data in Todd Creek
* Tables S3 - Model comparison using Widely Applicable Information Criterion
* Tables S4 - Parameter estimates from the Bayesian dispersal model
* Figures S1 - Frequency distributions for dispersal distance of bluehead chub
* Figures S2 - Frequency distributions for dispersal distance of creek chub
* Figures S3 - Frequency distributions for dispersal distance of striped jumprock

\pagebreak

### Table S1
```{r include = F, warning = F}
# Basic statistics
  # Library ----
  rm(list = ls(all.names = TRUE))
  library(stringr)
  library(knitr)

  # Function ----
  fmr <- function(dat){
    Mark_u <- tapply(dat$IND_ID, dat$Species, function(x) length(unique(x) ) )
    Recap_u <- tapply(dat$IND_ID[dat$Y==1], dat$Species[dat$Y==1],
                      function(x) length(unique(x) ) )
    Mark_repl <- tapply(dat$IND_ID, dat$Species, function(x) length(x) )
    Recap_repl <- tapply(dat$IND_ID[dat$Y==1], dat$Species[dat$Y==1],
                         function(x) length(x) )
    return(list(Mark_u = Mark_u, Recap_u = Recap_u,
                Mark_repl = Mark_repl, Recap_repl = Recap_repl) )
  }
  
  # Data ----
  # Fish data
  dat <- read.csv("data/VectorData_MERGE2019-11-19.csv")
  
  dat1 <- fmr(dat[dat$Stream=="Indian",])
  dat2 <- fmr(dat[dat$Stream=="Todd",])
  
  M1 <- data.frame(dat1$Mark_u, dat1$Recap_u, dat1$Mark_repl, dat1$Recap_repl)
  M2 <- data.frame(dat2$Mark_u, dat2$Recap_u, dat2$Mark_repl, dat2$Recap_repl)
  colnames(M2) <- colnames(M1) <- c("Individuals captured (unique)", "Individuals recaptured (unique)",
                                    "Individuals captured (total replicate)", "Individuals recaptured (total replicate)")
  
```

**Table S1** Descriptive statistics for the mark-recapture data of bluehead chub (BHC), creek chub (CRC) and striped jumprock (STJ) in Indian Creek. “Unique” individuals captured or recaptured are the number of individuals excluding repeated counts of the same individuals. “Total replicate” is the total number of individuals captured or recaptured including repeated counts of the same individuals.

```{r echo = F, warning = F}
kable(M1, format = "markdown")
```

\pagebreak

### Table S2
**Table S2** Descriptive statistics for the mark-recapture data of bluehead chub (BHC), creek chub (CRC) and striped jumprock (STJ) in Todd Creek. See Table S1 for details.
```{r echo = F, warning = F}
kable(M2, format = "markdown")
```

\pagebreak

### Table S3
**Table S3** Comparison of Widely Applicable Information Criterion (WAIC) between models that use high flows (the occurrence of flow events exceeding the 99th percentile of daily water levels) and median water levels as a metric of stream flow conditions. Species name abbreviations - **BHC**: bluehead chub, **CRC**: creek chub, **STJ**, striped jumprock
```{r echo = F}
M3 <- read.csv("result/WAIC_summary.csv")
colnames(M3) <- c("Species", "WAIC for the high flow model", "WAIC for the median flow model")
kable(M3)
```

\pagebreak

### Table S4
**Table S4** Parameter estimates from the Bayesian dispersal model that uses median water level as a measure of stream flows (instead of the occurrence of flow events that exceeded the 99th percentile of daily water levels during the whole study period). Posterior probability indicates the proportion of MCMC samples assigned to be either negative or positive (1500 MCMC samples were used to calculate posterior probabilities). Species name abbreviations - **BHC**: bluehead chub, **CRC**: creek chub, **STJ**, striped jumprock
```{r echo = F}
M4 <- read.csv("result/Est_MedFlowModel.csv")
M4$Effect <- as.character(M4$Effect)
colnames(M4) <- c("Species", "Effect", "Estimate", "Lower 95% CI", "Upper 95% CI")
M4[,3:5] <- round(M4[,3:5], 2)
M4[which(M4$Effect == "mu.phi"), "Effect"] <- "$\\mu_{\\phi}$"
M4[which(M4$Effect == "sigma.phi"), "Effect"] <- "$\\sigma_{\\phi}$"
kable(M4)
```

\pagebreak

### Figure S1
```{r echo = F}
# Data for figure S1-3
# Library ----
  rm(list = ls(all.names = TRUE))
  library(stringr)

# Data ----
  # Fish data
    dat <- read.csv("data/VectorData_MERGE2019-11-19.csv")
    dat$St_Month <- as.numeric(format(as.Date(dat$Date1), format = "%m") )
    dat$St_Year <- format(as.Date(dat$Date1), format = "%Y")
    dat$End_Month <- as.numeric(format(as.Date(dat$Date2), format = "%m") )
    dat$End_Year <- format(as.Date(dat$Date2), format = "%Y")
    
    ## Movement distance
    dat$X_m <- (dat$X2-dat$X1)*20 
    SP <- sort(unique(dat$Species) )
  
  # Env data
    QF99 <- read.csv("data/Env_QF99_2019-11-19.csv")
    Q99 <- cbind(QF99$QF99_Indian, QF99$QF99_Todd)
    Str <- ifelse(dat$Stream=="Indian", 1, 2)
    dat$QF99 <- Q99[cbind(dat$Occasion1, Str)]
    dat$Q99 <- ifelse(dat$QF99 > 0, 1, 0)
```

```{r echo = F}
# Plot ----
  for(i in 1){# select BHC
      par(mfrow = c(4, 4), mar = c(3,3,2,1), oma = c(1,2,0,0) )
      dd <- dat[dat$Species==SP[i],]
      sapply(1:length(unique(dd$Occasion1) ), function(x){
             ##plot
               plot(table(dd$X_m[dd$Occasion1 == x]),
                    axes = F, ann = F, col = ifelse(unique(dd$Q99[dd$Occasion1 == x]) >= 1, "red", "black"),
                    xlim = c(-max(abs(dd$X_m), na.rm = T),
                             max(abs(dd$X_m), na.rm = T) ) )
               legend("topright", bty = "n",
                      legend = substitute("N = "*v1, list(v1 = sum(dd$Y[dd$Occasion1 == x]) ) ) )
             ##panel label
               St_Month <- sort(unique(dd[dd$Occasion1 == x, "St_Month"]) )
               St_Year <- unique(dd[dd$Occasion1 == x, "St_Year"])
               End_Month <- sort(na.omit(unique(dd[dd$Occasion1 == x, "End_Month"]) ) )
               End_Year <- na.omit(unique(dd[dd$Occasion1 == x, "End_Year"]) )
               lab <- paste0(str_sub(month.name[St_Month[1]], 1, 3), "-", St_Year,
                            " to ",
                            str_sub(month.name[End_Month[1]], 1, 3), "-", End_Year)
               mtext(lab, 3, line = 0.5, cex = 0.8)
             ##axis
               sapply(1:2, function(z) axis(z, las = z) )
             })
      mtext("Dispersal distance (m)", 1, outer = T)
      mtext("Frequency", 2, outer = T)
  }

```

**Figure S1** Frequency distributions for dispersal distance of bluehead chub (*Nocomis leptocephalus*). Data from two streams (Indian and Todd Creeks) were combined. Each panel corresponds to a 2-month sampling interval. Red-colored panels are the sampling intervals with extreme flows exceeding the 99th percentile of daily water levels. Values shown on the top right of each panel (N) denote the number of recaptured individuals.

\pagebreak

### Figure S2
```{r echo = F}
# Plot ----
  for(i in 2){# select CRC
      par(mfrow = c(4, 4), mar = c(3,3,2,1), oma = c(1,2,0,0) )
      dd <- dat[dat$Species==SP[i],]
      sapply(1:length(unique(dd$Occasion1) ), function(x){
             ##plot
               plot(table(dd$X_m[dd$Occasion1 == x]),
                    axes = F, ann = F, col = ifelse(unique(dd$Q99[dd$Occasion1 == x]) >= 1, "red", "black"),
                    xlim = c(-max(abs(dd$X_m), na.rm = T),
                             max(abs(dd$X_m), na.rm = T) ) )
               legend("topright", bty = "n",
                      legend = substitute("N = "*v1, list(v1 = sum(dd$Y[dd$Occasion1 == x]) ) ) )
             ##panel label
               St_Month <- sort(unique(dd[dd$Occasion1 == x, "St_Month"]) )
               St_Year <- unique(dd[dd$Occasion1 == x, "St_Year"])
               End_Month <- sort(na.omit(unique(dd[dd$Occasion1 == x, "End_Month"]) ) )
               End_Year <- na.omit(unique(dd[dd$Occasion1 == x, "End_Year"]) )
               lab <- paste0(str_sub(month.name[St_Month[1]], 1, 3), "-", St_Year,
                            " to ",
                            str_sub(month.name[End_Month[1]], 1, 3), "-", End_Year)
               mtext(lab, 3, line = 0.5, cex = 0.8)
             ##axis
               sapply(1:2, function(z) axis(z, las = z) )
             })
      mtext("Dispersal distance (m)", 1, outer = T)
      mtext("Frequency", 2, outer = T)
  }

```

**Figure S2** Frequency distributions for dispersal distance of creek chub (*Semotilus atromaculatus*). Data from two streams (Indian and Todd Creeks) were combined. See Figure S1 for details.

\pagebreak

### Figure S3
```{r echo = F}
# Plot ----
  for(i in 3){# select STJ
      par(mfrow = c(4, 4), mar = c(3,3,2,1), oma = c(1,2,0,0) )
      dd <- dat[dat$Species==SP[i],]
      sapply(1:length(unique(dd$Occasion1) ), function(x){
             ##plot
               plot(table(dd$X_m[dd$Occasion1 == x]),
                    axes = F, ann = F, col = ifelse(unique(dd$Q99[dd$Occasion1 == x]) >= 1, "red", "black"),
                    xlim = c(-max(abs(dd$X_m), na.rm = T),
                             max(abs(dd$X_m), na.rm = T) ) )
               legend("topright", bty = "n",
                      legend = substitute("N = "*v1, list(v1 = sum(dd$Y[dd$Occasion1 == x]) ) ) )
             ##panel label
               St_Month <- sort(unique(dd[dd$Occasion1 == x, "St_Month"]) )
               St_Year <- unique(dd[dd$Occasion1 == x, "St_Year"])
               End_Month <- sort(na.omit(unique(dd[dd$Occasion1 == x, "End_Month"]) ) )
               End_Year <- na.omit(unique(dd[dd$Occasion1 == x, "End_Year"]) )
               lab <- paste0(str_sub(month.name[St_Month[1]], 1, 3), "-", St_Year,
                            " to ",
                            str_sub(month.name[End_Month[1]], 1, 3), "-", End_Year)
               mtext(lab, 3, line = 0.5, cex = 0.8)
             ##axis
               sapply(1:2, function(z) axis(z, las = z) )
             })
      mtext("Dispersal distance (m)", 1, outer = T)
      mtext("Frequency", 2, outer = T)
  }

```

**Figure S3** Frequency distributions for dispersal distance of striped jumprock (*Moxostoma rupicartes*). Data from two streams (Indian and Todd Creeks) were combined. See Figure S1 for details.

\pagebreak
